%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\vspace{-4.0mm}
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
{\vspace{-1.25mm}}

%---------------------------------------------------------
\cventry
    {Dec. 2019 - Present} % Job title
    {Consultant-Data Engineering, Accenture} % Organization
    {New York, NY, USA} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Business \& Data Strategy Architect at a leading network \& communications client. Used Python, PostGreSQL, Airflow, Consul to architect and build out ETL processes for Video Spectrum Optimization}
        \item {Data Integration Engineer at a Healhcare client- Used Talend, SQLServer to build jobs for data migration between legacy and SAP systems}
        \item {Data Engineer at a Real Estate Development client- Used python and SQL to develop ETL validation framework comparison tool}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Apr. 2019 - Nov. 2019} % Job title
    {Data Engineer, National Center for Supercomputing Applications} % Organization
    {Urbana, IL, USA} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Used machine learning to perform analysis of applications running on the Blue Waters supercomputer and identifying areas for improvement}
        \item{Developed code for high performance computing using parallel programming to obfuscate private information from system log files (10TB)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Jan. 2018 - Dec. 2018} % Job title
    {Data Science Analyst, Deere and Company (John Deere)} % Organization
    {Champaign, IL, USA} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Achieved an accuracy of 87\% in predicting engine performance outcomes from approx 10,000 machines, 560 billion rows (14 TB) of a database}
        \item {Identified actionable improvements in the manufacturing \& design of machines using hypothesis testing and predictive modeling}
        %\item {Delivered predictive models for crop yield estimation, event detection and prediction on unbalanced datasets}
        %\item {Worked with the Robotics team, used GPS, lidar data and computer vision to make the robotic lawn mower (Tango) identify its location}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Jan. 2018 - May 2018} % Job title
    {Project Manager, Business Intelligence Group at UIUC} % Organization
    {Champaign, IL, USA} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item { Led a team of 5 consultants to provide consulting services to a Fortune 500 client which ultimately led to a revamped intranet portal}
        \item { Managed strict project timelines and requirements successfully by conducting in-person and virtual meetings with multiple stakeholders}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Sep. 2017 - Jan. 2018} % Job title
    {Assistant to the sales director (Social Media \& Web Analytics), Illini Media Company} % Organization
    {Champaign, IL, USA} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Analyzed sales \& marketing campaign data, website click-throughs, page impressions for 4 sub-companies using Google Analytics}
        \item {Prepared \& presented dashboards and reports to improve sales force effectiveness}
      \end{cvitems}
    }

%---------------------------------------------------------
  
  \cventry
    {Jun. 2014 - Jun 2017} % Job title
    {Deputy Manager- Business Development, Siemens Financial Services Pvt. Ltd.} % Organization
    {Mumbai, MH, India} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed innovative solutions to enhance sales force effectiveness while consistently exceeding business dev. targets by 150\% YoY}
        %\item {Led region south in an effort to develop business using a consultative approach while customizing solutions based on client requirements}
        %\item {Consistently exceeded business development targets: by 200\% in FY 2016-17, by 130\% in FY 2015-16 and by 140\% in FY 2014-15}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
\vspace{-4.5mm}